---
title: "CBDA-SL and Knockoff Filter Results on the ADNI Dataset - 9000 jobs x 9 experiments"
author: "Simeone Marino"
date: "January 2, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Some useful information

This is a summary of a set of 9 experiments I ran on Cranium using a single pipe workflow file that performs 3000 independent jobs, each one with the CBDA-SL and the knockoff filter feature mining strategies.
Each experiments has a total of 9000 jobs and is uniquely identified by 6 input arguments: # of jobs [M], % of missing values [misValperc], min [Kcol_min] and max [Kcol_max] % for FSR-Feature Sampling Range, min [Nrow_min] and max [Nrow_max] % for SSR-Subject Sampling Range.

This document has the final results, by experiment. See <https://drive.google.com/file/d/0B5sz_T_1CNJQWmlsRTZEcjBEOEk/view?ths=true> for some general documentation of the CBDA-SL project and github <https://github.com/SOCR/CBDA> for some of the code [still in progress].

```{r Loading the ADNI Dataset, include=TRUE}
# # Here I load the dataset [not executed]
# ADNI_dataset = read.csv("C:/Users/simeonem/Documents/CBDA-SL/Cranium/ADNI_dataset.txt",header = TRUE)

```

Features selected by both the knockoff filter and the CBDA-SL algorithms are shown as spikes in
the histograms shown below. No False Discovery Rates are shown (since we don't have information on the "true" features). I list the top features selected, set to 15 here.

```{r Set the location of the arguments file and the workspace directory, echo=FALSE}
arg_file = as.array('C:/Users/simeonem/Documents/CBDA-SL/Cranium/arg_ADNI.txt')
#workspace_directory<-setwd("C:/Users/simeonem/Documents/CBDA-SL/ExperimentsNov2016/KO/Dec5/")
workspace_directory<-c("C:/Users/simeonem/Documents/CBDA-SL/ExperimentsNov2016/ADNI/")
eval(parse(text=paste0("knitr::opts_knit$set(root.dir = '",workspace_directory,"')")))
library("caret")
#opts_knit$set(root.dir = 'c:/Users/kwilliams/git/ProjectX')

```
```{r Read the input arguments and the dataset from the specified file, echo=FALSE}
eval(parse(text=paste0("arguments <- read.table(arg_file, header = TRUE)")))
```

```{r Set the list of experiments to analze, echo=FALSE}
#list_exps=1:dim(arguments)[1]; # all the experiments
#list_exps=list_exps[-1*c(21)] # the experiments to exclude
#list_exps = 1:12
list_exps = c(1:9)
```

```{r Save basic info in a temp file to speed up the script while looping through the experiments, echo=FALSE}
label=c("ADNI_dataset")
eval(parse(text=paste0("save(arguments,workspace_directory,list_exps,label,file= \"~/temp_ADNI.RData\")")))
```

```{r Loop through each experiment to load the workspace and generate histograms/tables, echo=FALSE}
for (i in list_exps) {
  print(paste("EXPERIMENT",i),quote = FALSE)
print.table(arguments[i,])
#print(i)
  # print(workspace_directory)
  # print(arguments)
  M <-arguments[i,1]
  misValperc <- arguments[i,2]
  Kcol_min <- arguments[i,3]
  Kcol_max <- arguments[i,4]
  Nrow_min <- arguments[i,5]
  Nrow_max <- arguments[i,6]
  range_n <- eval(parse(text=paste0("c(\"",Nrow_min,"_",Nrow_max,"\")")))
  range_k <- eval(parse(text=paste0("c(\"",Kcol_min,"_",Kcol_max,"\")")))
  
  eval(parse(text=paste0("load(\"",workspace_directory,"/CBDA_SL_M",M,"_miss",misValperc,"_n",range_n,"_k",range_k,"_Light_",label,".RData\")")))
  
# GENERATE HISTOGRAM OF THE CUMULATIVE KNOCKOFF RESULTS FOR SINGLE EXPERIMENT
x = KO_sub;
eval(parse(text=paste0("h=hist(x, plot = FALSE ,breaks=seq(min(x)-0.5, max(x)+0.5, by=1))")))
h$density = h$counts/sum(h$counts)*100
title_temp <- c("KNOCKOFF FILTER RESULTS")
#print(title_temp)
plot(h,freq=FALSE,ylab='Density (%)',xlab='Feature #',main = title_temp,ylim=c(0,max(h$density)))

# GENERATE HISTOGRAM OF THE TOP # OF COVARIATES FOR SINGLE EXPERIMENT
#print(arguments[i,])
eval(parse(text=paste0("x = k_top_",top,"_temp")))
eval(parse(text=paste0("h=hist(k_top_",top,"_temp, plot = FALSE ,breaks=seq(min(k_top_",top,"_temp)-0.5, max(k_top_",top,"_temp)+0.5, by=1))")))
h$density = h$counts/sum(h$counts)*100
title_temp <- c("CBDA-SL RESULTS")
#print(title_temp)
plot(h,freq=FALSE,ylab='Density (%)',xlab='Feature #',main = title_temp,ylim=c(0,max(h$density)))
#readline("Press <return to continue")

top=20;
qa <-as.data.frame(Top_features[1:top])
names(qa) <- c("CBDA-Feature","Frequency")
qa$Density <- 100*(qa$Frequency/sum(Top_features))
print("TABLE with CBDA-SL & KNOCKOFF FILTER RESULTS")
# print(c("EXPERIMENT",i))
# print(arguments[i,])

Top_Knockoff_features=sort(table(KO_sub), decreasing = TRUE)
Top_Knockoff_features_labels <- as.numeric(names(Top_Knockoff_features)[1:top])
qa$Knockoff <- Top_Knockoff_features_labels
qa$KO_Density <- 100*(Top_Knockoff_features[1:top]/sum(Top_Knockoff_features))
names(qa) <- c("CBDA","Frequency","Density","Knockoff","Density")
top=15; # how many top rows to show and use to calculate FDRs
print(qa[1:top,], right = FALSE, row.names = FALSE)
# FDR_CBDA <- 100*(1 - sum(!is.na(match(qa$CBDA[1:top],nonzero)))/top)
# FDR_KO <- 100*(1 - sum(!is.na(match(qa$Knockoff[1:top],nonzero)))/top)
# a1=round(FDR_CBDA,digits=3)
# a2=round(FDR_KO,digits=3)
#print(paste("False Discovery Rate for CBDA = ",a1,"%"),quote = FALSE)
#writeLines(c("False Discovery Rate for CBDA [%]",a1))
#print(paste("False Discovery Rate for KNOCKOFF FILTER = ",a2,"%"),quote = FALSE)
rm(list = ls())
eval(parse(text=paste0("load(\"~/temp_ADNI.RData\")")))
cat("\n\n\n\n\n\n")
}
```

